A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-06-29 tex-arxiv/article.tex
fix conclusions
small fix to abstract

\begin{abstract}
	Imitation Learning is a discipline of Machine Learning primarily concerned with replicating observed behavior of agents known to perform well on a given task, collected in demonstration data sets. In this paper, we set out to introduce a pipeline for collecting demonstrations and training models that can produce motion plans for industrial robots. Object throwing is defined as the motivating use case. Multiple input data modalities are surveyed, and motion capture is selected as the most practicable. Two model architectures operating autoregressively are examined -- feedforward and recurrent neural networks. Trained models execute throws on a real robot successfully, and a battery of quantitative evaluation metrics is proposed, including extrapolated throw accuracy estimates. Recurrent neural networks outperform feedforward ones in most respects, with the best models having an assessed mean throw error on the order of 0.1-0.2m at distances of 1.5-2m. The data collection, pre-processing, and model training aspects of our proposed approach show promise, but further work is required in developing Cartesian motion planning tools before it is applicable in production applications.
\end{abstract}

@@

Potential directions for further research and engineering work based on what we have achieved thus far would be:
\begin{itemize}
	\item replacement of simple feedforward neural networks with generative adversarial models, which demonstrate some of the best performance for pure Markovian policies \citep{ho2016generative}. This way the need for more compute-intensive sequence-to-sequence models that necessitate keeping track of state histories may be obviated;
	\item adapting the pipeline for other tasks of interest, mainly to explore how easily the data pre-processing pipeline generalizes in practice;
	\item train models to predict velocities as the actions, rather than subsequent states, for integration with servo controllers;
	\item development of a Cartesian arrival time-based time parametrization tool in ROS, something which is currently lacking in the ecosystem.
\end{itemize}

>>>>

\begin{abstract}
	Imitation Learning is a discipline of Machine Learning primarily concerned with replicating observed behavior of agents known to perform well on a given task, collected in demonstration data sets. In this paper, we set out to introduce a pipeline for collecting demonstrations and training models that can produce motion plans for industrial robots. Object throwing is defined as the motivating use case. Multiple input data modalities are surveyed, and motion capture is selected as the most practicable. Two model architectures operating autoregressively are examined -- feedforward and recurrent neural networks. Trained models execute throws on a real robot successfully, and a battery of quantitative evaluation metrics is proposed, including extrapolated throw accuracy estimates. Recurrent neural networks outperform feedforward ones in most respects, with the best models having an assessed mean throw error on the order of 0.1...0.2m at distances of 1.5...2.0m. The data collection, pre-processing, and model training aspects of our proposed approach show promise, but further work is required in developing Cartesian motion planning tools before it is applicable in production applications.
\end{abstract}

@@

Potential directions for further research and engineering work based on what we have achieved thus far would be:
\begin{itemize}
	\item replacement of simple feedforward neural networks with generative adversarial models, which demonstrate some of the best performance for pure Markovian policies \citep{ho2016generative}. This way the need for more compute-intensive sequence-to-sequence models that necessitate keeping track of state histories may be obviated;
	\item adapting the pipeline for other tasks of interest, mainly to explore how easily the data pre-processing pipeline generalizes in practice;
	\item train models to predict velocities as the actions, rather than subsequent states, for integration with servo controllers;
	\item development of a Cartesian arrival-time parametrization tool in ROS, something which is currently lacking in the ecosystem.
\end{itemize}
